---
title: "Dummy Notes"
author: "Collins"
date: "02/04/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234) # for reproducibility 
```

# Introduction

Hypothesis: 
People with a second language have a broader definitions
because they are able to add definitions from another language.
Having broader definitions may mean that second language speaks
are able to find relationships between concepts
that single language speakers are unable to find.

Why choose coffee and cake?
It is a trans-cultural experience which has a flexible definition.

## Import dummy data

```{r import}
dummy_data <- read.csv("dummy-data.csv", header = TRUE)
dummy_data[,'gender']<-factor(dummy_data[,'gender'])
```

## Take a look the participants

Gender balance.

```{r pie}
library(ggplot2)
ggplot(dummy_data, aes(x=factor(1), fill=gender))+
  geom_bar(width = 1)+
  coord_polar("y")
```

## T Test


```{r ttest}
set.seed(2820)
preTreat <- c(rnorm(1000, mean = 145, sd = 9))
postTreat <- c(rnorm(1000, mean = 138, sd = 8))
t.test(preTreat, postTreat, paired = TRUE)
```

## Word clouds

```{r cloud-libraries}
library(tidyverse)
library(RColorBrewer)
library(wordcloud)
```


### For Pick a Word

Word cloud from the pick lists.

```{r pick-cloud}
pick_columns = dummy_data %>% select(8:28)
pick_counts = colSums(pick_columns)
pick_counts =  as.data.frame(as.table(pick_counts))
wordcloud(words=pick_counts$Var1, freq=pick_counts$Freq,
          max.words=12, random.order=FALSE,
          min.freq=4, colors=brewer.pal(8, "Dark2"))
```

### For Cloze Procedure

Word cloud from the Anna Karenina extract.

```{r cloze-cloud}
cloze_column = as.matrix(dummy_data[,c("q1", "q2", "q3", "q4", "q5")])
cloze_words = as.vector(cloze_column)
cloze_counts = table(cloze_words)
cloze_counts = as.data.frame(cloze_counts)
wordcloud(words=cloze_counts$cloze_words, freq=cloze_counts$Freq, 
          colors=brewer.pal(8, "Dark2"))
```

