---
title: "Coffee, Cake, Culture and Cognition"
author: "Collins"
date: "02/04/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Hypothesis: 
People with a second language have a broader definitions
because they are able to add definitions from another language.
Having broader definitions may mean that second language speaks
are able to find relationships between concepts
that single language speakers are unable to find.

Why choose coffee and cake?
It is a trans-cultural experience which has a flexible definition.

## Import dummy data

```{r import}
df <- read.csv("data.csv", header = TRUE)
df[,'gender']<-factor(df[,'gender'])
```

## Take a look

Ensure that the sample is balanced.

```{r pie}
library(ggplot2)
ggplot(df, aes(x=factor(1), fill=gender))+
  geom_bar(width = 1)+
  coord_polar("y")
```

## T Test


```{r ttest}
set.seed(2820)
preTreat <- c(rnorm(1000, mean = 145, sd = 9))
postTreat <- c(rnorm(1000, mean = 138, sd = 8))
t.test(preTreat, postTreat, paired = TRUE)
```
