---
title: "Dummy Data Demo Notes"
author: "Collins"
date: "02/04/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=8, fig.height=5) 
set.seed(1234) # for reproducibility 
```

# Introduction

> To have another language is to possess a second soul.

Charlemagne

## Hypothesis 

People with a second language have a broader definitions
because they are able to add definitions from another language.
Having broader definitions may mean that second language speaks
are able to find relationships between concepts
that single language speakers are unable to find.

## Why choose coffee and cake?

It is a trans-cultural experience which has a flexible definition.

## Import dummy data

```{r import}
questionnaire_data <- read.csv("questionnaire-data.csv", header = TRUE)
questionnaire_data[,'gender']<-factor(questionnaire_data[,'gender'])
```

## Take a look the participants


### Age distribution

```{r ages}
mean_age = mean(questionnaire_data$age, trim = 0, na.rm = FALSE)
hist(questionnaire_data$age)
```

Average age is ``r mean_age``.
Largely middle aged sample.

### Gender balance

```{r gender}
gender = table(questionnaire_data$gender)
pie(gender)
```

The sample was selected to be gender balanced.

```{r languages}
languages <- table(questionnaire_data$language)
languages
```

Mostly North European.

## Are the two groups different?

Sum up the multiple select so we know the total number of words each participant
selected.
Then split the data into those who speak a second language and those that do no.

```{r split}
questionnaire_data$total_selected = rowSums(questionnaire_data[,c("Agreeable", "Creative",
                                                  "Determined", "Energetic",
                                                  "Funny", "Polite", "Kind",
                                                  "Arrogant", "Cruel", "Grumpy",
                                                  "Impatient", "Jealous",
                                                  "Rude", "Unhappy", "Bold",
                                                  "Fierce", "Meticulous",
                                                  "Restless", "Sly",
                                                  "Talkative", "Unpredictable")])
monolinguals = questionnaire_data[questionnaire_data$bilingual == 0, ]
bilinguals = questionnaire_data[questionnaire_data$bilingual != 0, ]
```
### Difference in Rating

Or do bilinguals and monolinguals rate coffee and cake differently.
Or do they hold difference concepts of coffee and cake.
Using T test because the sample size is so small.
This assumes that the two groups are normally distributed
and the variances of the two groups are equal.

```{r ratings}
t.test(bilinguals$fat.thin, monolinguals$fat.thin, paired = FALSE)
t.test(bilinguals$funny.sad, monolinguals$funny.sad, paired = FALSE)
t.test(bilinguals$red.green, monolinguals$red.green, paired = FALSE)
t.test(bilinguals$horrible.fantastic, monolinguals$horrible.fantastic, paired = FALSE)
t.test(bilinguals$stupid.intellectual, monolinguals$stupid.intellectual, paired = FALSE)
t.test(bilinguals$sparkling.still, monolinguals$sparkling.still, paired = FALSE)
```

There is no significant difference in how monolinguals and bilinguals rated
their coffee and cake experience.

### Difference in Totals

If the hypothesis is correct that bilinguals have a broader concept of coffee and cake,
then one would expect them to select more words from the constrained word list.
The expectation is that the bilingual mean will be greater,
so this is a one-tailed test.


```{r multiple-select}
bilingual_selected = mean(bilinguals$total_selected, trim = 0, na.rm = FALSE)
monolingual_selected = mean(monolinguals$total_selected, trim = 0, na.rm = FALSE)
t.test(bilinguals$total_selected, monolinguals$total_selected, paired = FALSE, alternative = "greater")

```

There is a big difference in means, significant at a 90% level.
Looks like bilinguals have a bigger concept of coffee and cake.

## Word clouds

```{r cloud-libraries}
library(tidyverse)
library(RColorBrewer)
library(wordcloud)
```


### For Pick a Word

Word cloud from the multiple select list.
Showing consistently selecting the positive words.

```{r pick-cloud}
pick_columns = questionnaire_data %>% select(8:28)
pick_counts = colSums(pick_columns)
pick_counts =  as.data.frame(as.table(pick_counts))
wordcloud(words=pick_counts$Var1, freq=pick_counts$Freq,
          max.words=12, random.order=FALSE,
          min.freq=4, colors=brewer.pal(8, "Dark2"))
```

### For Cloze Procedure

Word cloud from the Anna Karenina extract.

```{r cloze-cloud}
cloze_column = as.matrix(questionnaire_data[,c("q1", "q2", "q3", "q4", "q5")])
cloze_words = as.vector(cloze_column)
cloze_counts = table(cloze_words)
cloze_counts = as.data.frame(cloze_counts)
wordcloud(words=cloze_counts$cloze_words, freq=cloze_counts$Freq, 
          colors=brewer.pal(8, "Dark2"))
```

