---
title: "Questionnaire Results"
output: pdf_document
---
> To have another language is to possess a second soul - Charlemagne

# Hypothesis 

People with a second language have a broader definitions
because they are able to add definitions from another language.

## Why choose coffee and cake?

It is a cross-cultural experience which has a flexible definition.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=7, fig.height=4.5) 
set.seed(1234) # for reproducibility 
questionnaire_data <- read.csv("questionnaire-data.csv", header = TRUE)
questionnaire_data[,'gender']<-factor(questionnaire_data[,'gender'])
```

# Take a look the participants

```{r ages}
mean_age = mean(questionnaire_data$age, trim = 0, na.rm = FALSE)
hist(questionnaire_data$age, 
     main="Age Distribution", 
     xlab="Age in Years", 
     ylab="Count",
     col="darkmagenta",
     freq=TRUE
     )
```

Average age is ``r round(mean_age, digits = 1)``.
Largely middle aged sample.

```{r gender}
gender = table(questionnaire_data$gender)
pie(gender, 
    c("Female", "Male"),
    main = "Gender Balance", 
    col = rainbow(length(gender))
    )
```

The sample was selected to be gender balanced.

```{r languages}
languages <- table(questionnaire_data$language)
languages
```

Mostly North European languages with strong coffee and cake cultures

# Are the two groups different?

Sum up the multiple select
so we know the total number of words each participant selected.
Then split the data into those who speak a second language and those that do not.

```{r split}
questionnaire_data$total_selected = rowSums(questionnaire_data[,c(
    "Agreeable", "Creative","Determined", "Energetic","Funny", "Polite", "Kind",
    "Arrogant", "Cruel", "Grumpy", "Impatient", "Jealous","Rude", "Unhappy",
    "Bold", "Fierce", "Meticulous", "Restless", "Sly", "Talkative", "Unpredictable")])
questionnaire_data$total_selected_positive = rowSums(questionnaire_data[,c(
    "Agreeable", "Creative","Determined", "Energetic","Funny", "Polite", "Kind")])
questionnaire_data$total_selected_negative = rowSums(questionnaire_data[,c(
    "Arrogant", "Cruel", "Grumpy", "Impatient", "Jealous","Rude", "Unhappy")])
questionnaire_data$total_selected_neutral = rowSums(questionnaire_data[,c(
    "Bold", "Fierce", "Meticulous", "Restless", "Sly", "Talkative", "Unpredictable")])
monolinguals = questionnaire_data[questionnaire_data$bilingual == 0, ]
bilinguals = questionnaire_data[questionnaire_data$bilingual != 0, ]
```

## Difference in Rating

Or do bilinguals and monolinguals rate coffee and cake differently.
Or do they hold difference concepts of coffee and cake.
Using T test because the sample size is so small.
This assumes that the two groups are normally distributed
and the variances of the two groups are equal.

```{r ratings}
t.test(bilinguals$fat.thin, monolinguals$fat.thin, paired = FALSE)
t.test(bilinguals$funny.sad, monolinguals$funny.sad, paired = FALSE)
t.test(bilinguals$red.green, monolinguals$red.green, paired = FALSE)
t.test(bilinguals$horrible.fantastic, monolinguals$horrible.fantastic, paired = FALSE)
t.test(bilinguals$stupid.intellectual, monolinguals$stupid.intellectual, paired = FALSE)
t.test(bilinguals$sparkling.still, monolinguals$sparkling.still, paired = FALSE)
```

There is no significant difference in how monolinguals and bilinguals rated
their coffee and cake experience.

## Difference in Totals

If the hypothesis is correct that bilinguals have
a broader concept of coffee and cake,
then one would expect them to select more words from the constrained word list.
The expectation is that the bilingual mean will be greater,
so this is a one-tailed test.


```{r multiple-select}
t.test(bilinguals$total_selected, monolinguals$total_selected,
       paired=FALSE, alternative="greater")
```

Indeed there is a significant difference between
the monolinguals and the bilinguals,
in the total number of words selected.
Bilinguals choosing an expanded list.

The words were grouped into positive, negative and neutral words.
The difference in the number of words selected
was not significant for the negative and neutral words,
but was for the positive words.

```{r multiple-select-positive}
t.test(bilinguals$total_selected_positive,
       monolinguals$total_selected_positive,
       paired=FALSE, alternative="greater")
```

This is what drives the significant difference in the total number
of words selected.


## Word clouds

```{r cloud-libraries}
library(tidyverse)
library(RColorBrewer)
library(wordcloud)
```


### For Pick a Word

Word cloud from the multiple select list.
Showing consistently selecting the positive words.

```{r pick-cloud}
pick_columns = questionnaire_data %>% select(8:28)
pick_counts = colSums(pick_columns)
pick_counts =  as.data.frame(as.table(pick_counts))
wordcloud(words=pick_counts$Var1, freq=pick_counts$Freq,
          max.words=12, random.order=FALSE,
          min.freq=4, colors=brewer.pal(8, "Dark2"))
```

### For Cloze Procedure

Word cloud from the Anna Karenina extract.

```{r cloze-cloud}
cloze_column = as.matrix(questionnaire_data[,c("q1", "q2", "q3", "q4", "q5")])
cloze_words = as.vector(cloze_column)
cloze_counts = table(cloze_words)
cloze_counts = as.data.frame(cloze_counts)
wordcloud(words=cloze_counts$cloze_words, freq=cloze_counts$Freq, 
          colors=brewer.pal(8, "Dark2"))
```

The only word that was repeated was Red.

