---
title: "Coffee, Cake and Culture"
output:
  word_document: default
  pdf_document: default
---
> To have another language is to possess a second soul - Charlemagne

# Hypothesis 

People with a second language have a broader concept of coffee and cake,
because they combine their concepts from both languages.

## Why Choose Coffee and Cake?

It is a cross-cultural experience which has an imprecise definition.
Thus it is open to interpretation by participants in the study.

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=7, fig.height=4.5) 
set.seed(1234) # for reproducibility 
# Import the data
questionnaire_data <- read.csv("questionnaire-data.csv", header = TRUE)
questionnaire_data[,'gender']<-factor(questionnaire_data[,'gender'])
# Sum up the yes/no selected words.
questionnaire_data$total_selected = rowSums(questionnaire_data[,c(
    "Agreeable", "Creative","Determined", "Energetic","Funny", "Polite", "Kind",
    "Arrogant", "Cruel", "Grumpy", "Impatient", "Jealous","Rude", "Unhappy",
    "Bold", "Fierce", "Meticulous", "Restless", "Sly", "Talkative", "Unpredictable")])
questionnaire_data$total_selected_positive = rowSums(questionnaire_data[,c(
    "Agreeable", "Creative","Determined", "Energetic","Funny", "Polite", "Kind")])
questionnaire_data$total_selected_negative = rowSums(questionnaire_data[,c(
    "Arrogant", "Cruel", "Grumpy", "Impatient", "Jealous","Rude", "Unhappy")])
questionnaire_data$total_selected_neutral = rowSums(questionnaire_data[,c(
    "Bold", "Fierce", "Meticulous", "Restless", "Sly", "Talkative", "Unpredictable")])
# Divide the participants between mono and bilinguals.
monolinguals = questionnaire_data[questionnaire_data$bilingual == 0, ]
bilinguals = questionnaire_data[questionnaire_data$bilingual != 0, ]
```

## The Approach

An experimenter supervised questionnaire was administered
to ``r nrow(questionnaire_data)`` volunteer participants.
The questionnaire was supervised to ensure 
a reasonable completion rate
and to ensure the participants understood the questions being asked.
In in the event
some of the questions were challenging for the participants to understand.
If a similar questionnaire were to be administered without supervision
it would need further refinement to allow the participants to complete
it successfully.

The questionnaire consisted of 3 parts.

1. Rating Scales - participants were asked to rate 
   their coffee and cake experience on 7 arbitrary scales.
1. Word Assignment - participants were asked to indicate which words from a list
   (7 positive, 7 negative and 7 neutral) 
   could be applied to their coffee and cake experience.
1. A Cloze Procedure - participants were asked to fill in the blanks
   in a sentence from Tolstoy's 'Anna Karenina'.


# The Participants

The participants were all volunteers
selected from the experimenter's friends and family.
This is an undoubtedly biased sample, 
but using an entirely randomly selected sample
would have been too complicated and costly.

## Age

```{r}
mean_age = mean(questionnaire_data$age, trim = 0, na.rm = FALSE)
```

Average age is ``r round(mean_age, digits = 1)``.
So the sample is largely middle aged and post retirment.

```{r}
hist(questionnaire_data$age, 
     main = "",
     xlab="Age in Years", 
     ylab="Count",
     col="darkmagenta",
     freq=TRUE
     )
```

## Gender

The sample was intended to be gender balanced,
but ended up with more females.

```{r}
gender = table(questionnaire_data$gender)
pie(gender, 
    c("Female", "Male"),
    main = "", 
    col = rainbow(length(gender))
    )
```

## Second Language

A total of ``r nrow(questionnaire_data)`` participants took part in the study,
``r nrow(monolinguals)`` of whom spoke only English
and
``r nrow(bilinguals)``of whom spoke English and one other language.

Mostly North European languages with strong coffee and cake cultures.
Half the participants were bilingual and half were monolingual.
Unsurprisingly given that the study was conducted in England,
the second languages spoken were all from Northern European nations.

```{r}
languages <- table(questionnaire_data$language)
languages
```

# Do the two groups have different concepts of coffee and cake?

The data were split the data into those who speak a second language
and those that do not.

## Difference in Rating

Participants found rating their coffee and cake experience 
on a set of arbitrary scales challenging.
Some of the scales made no obvious sense to the participants
so placing a numerical value against that scale 
was equally non-sensical.
It was necessary to encourage participants to attempt an 'intuitive'
or 'gut feeling' response.

The hypothesis was that participants with a second language would
have a broader concept of their coffee and cake experience.
This would be expected to show up with the participants with a second language,
providing more variable ratings for their coffee and cake experience.
Whilst those with a single language might consistently
rate their coffee and cake experience at one end of the scale.

As can see seen below,
in every case there is little or nothing to distinguish between
the two groups of participants.
This is confirmed by means of an F-test.

It may be that participants were choosing a random number to be able to answer the question.
However, this was not evident during the administration of the questionnaire.
Each of the participants appear to give the rating scales some thoughtful consideration.
This is born out in the distributions shows below,
in that they do not appear to be random
and the two groups of participants appear to be consistent.

It would seem that when forced to rate their coffee and cake experience,
both those with a second language and those without rate
their experience similarly.

```{r}
# Double histogram for comparing the rating scales
library("colorspace") # for lighten and darken
double.histogram <- function(monolingual.scale, bilingual.scale, colour="blue") 
{
    par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
    monolingual.breaks <- seq(min(monolingual.scale)-0.5, max(monolingual.scale)+0.5, by=1)
    monolingual.colour <- lighten(colour, 0.4)
    hist(monolingual.scale,
         breaks=monolingual.breaks,
         col=monolingual.colour,
         freq=TRUE,
         main="No Second Language",
         xlab="",
         xlim=c(1,7),
         ylim=c(0,4)
         )
    bilingual.breaks <- seq(min(bilingual.scale)-0.5, max(bilingual.scale)+0.5, by=1)
    bilingual.colour <- darken(colour, 0.4)
    hist(bilingual.scale,
         breaks=bilingual.breaks,
         col=bilingual.colour,
         freq=TRUE,
         main="With Second Language",
         xlab="",
         xlim=c(1,7),
         ylim=c(0,4)
         )
}
```

### Hot-Cold

```{r}
double.histogram(monolinguals$cold.hot, bilinguals$cold.hot, "violet")
var.test(monolinguals$cold.hot, bilinguals$cold.hot, alternative = "two.sided")
```

### Fat-Thin

```{r}
double.histogram(monolinguals$fat.thin, bilinguals$fat.thin, "purple")
var.test(monolinguals$fat.thin, bilinguals$fat.thin, alternative = "two.sided")
```

### Funny-Sad

```{r}
double.histogram(monolinguals$funny.sad, bilinguals$funny.sad, "blue")
var.test(monolinguals$funny.sad, bilinguals$funny.sad, alternative = "two.sided")
```

### Red-Green

```{r}
double.histogram(monolinguals$red.green, bilinguals$red, "green")
var.test(monolinguals$red.green, bilinguals$red, alternative = "two.sided")
```

### Horrible-Fantastic

```{r}
double.histogram(monolinguals$horrible.fantastic, bilinguals$horrible.fantastic, "yellow")
var.test(monolinguals$horrible.fantastic, bilinguals$horrible.fantastic, alternative = "two.sided")
```

### Stupid-Intellectual

```{r}
double.histogram(monolinguals$stupid.intellectual, bilinguals$stupid.intellectual, "orange")
var.test(monolinguals$stupid.intellectual, bilinguals$stupid.intellectual, alternative = "two.sided")
```

### Sparkling-Still

```{r}
double.histogram(monolinguals$sparkling.still, bilinguals$sparkling, "red")
var.test(monolinguals$sparkling.still, bilinguals$sparkling, alternative = "two.sided")
```

## 

If the hypothesis is correct that bilinguals have
a broader concept of coffee and cake,
then one would expect them to select more words from the constrained word list.
The expectation is that the bilingual mean will be greater,
so this is a one-tailed test.


```{r multiple-select}
t.test(bilinguals$total_selected, monolinguals$total_selected,
       paired=FALSE, alternative="greater")
```

Indeed there is a significant difference between
the monolinguals and the bilinguals,
in the total number of words selected.
Bilinguals choosing an expanded list.

The words were grouped into positive, negative and neutral words.
The difference in the number of words selected
was not significant for the negative and neutral words,
but was for the positive words.

```{r multiple-select-positive}
t.test(bilinguals$total_selected_positive,
       monolinguals$total_selected_positive,
       paired=FALSE, alternative="greater")
```

This is what drives the significant difference in the total number
of words selected.


## Word clouds

```{r cloud-libraries}
library(tidyverse)
library(RColorBrewer)
library(wordcloud)
```


### For Pick a Word

Word cloud from the multiple select list.
Showing consistently selecting the positive words.

```{r pick-cloud}
pick_columns = questionnaire_data %>% select(8:28)
pick_counts = colSums(pick_columns)
pick_counts =  as.data.frame(as.table(pick_counts))
wordcloud(words=pick_counts$Var1, freq=pick_counts$Freq,
          max.words=12, random.order=FALSE,
          min.freq=4, colors=brewer.pal(8, "Dark2"))
```

### For Cloze Procedure

Word cloud from the Anna Karenina extract.

```{r cloze-cloud}
cloze_column = as.matrix(questionnaire_data[,c("q1", "q2", "q3", "q4", "q5")])
cloze_words = as.vector(cloze_column)
cloze_counts = table(cloze_words)
cloze_counts = as.data.frame(cloze_counts)
wordcloud(words=cloze_counts$cloze_words, freq=cloze_counts$Freq, 
          colors=brewer.pal(8, "Dark2"))
```

The only word that was repeated was Red.

