---
title: "Coffee, Cake and Culture"
output:
  pdf_document: default
  word_document: default
---
> To have another language is to possess a second soul - Charlemagne

# Hypothesis 

People with a second language have a broader concept of coffee and cake,
because they combine their concepts from both languages.

## Why Choose Coffee and Cake?

It is a cross-cultural experience which has an imprecise definition.
Thus it is open to interpretation by participants in the study.

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=7, fig.height=4.5) 
set.seed(1234) # for reproducibility 
# Import the data
questionnaire_data <- read.csv("questionnaire-data.csv", header = TRUE)
questionnaire_data[,'gender']<-factor(questionnaire_data[,'gender'])
# Sum up the yes/no selected words.
questionnaire_data$total_selected = rowSums(questionnaire_data[,c(
    "Agreeable", "Creative","Determined", "Energetic","Funny", "Polite", "Kind",
    "Arrogant", "Cruel", "Grumpy", "Impatient", "Jealous","Rude", "Unhappy",
    "Bold", "Fierce", "Meticulous", "Restless", "Sly", "Talkative", "Unpredictable")])
questionnaire_data$total_selected_positive = rowSums(questionnaire_data[,c(
    "Agreeable", "Creative","Determined", "Energetic","Funny", "Polite", "Kind")])
questionnaire_data$total_selected_negative = rowSums(questionnaire_data[,c(
    "Arrogant", "Cruel", "Grumpy", "Impatient", "Jealous","Rude", "Unhappy")])
questionnaire_data$total_selected_neutral = rowSums(questionnaire_data[,c(
    "Bold", "Fierce", "Meticulous", "Restless", "Sly", "Talkative", "Unpredictable")])
# Divide the participants between mono and bilinguals.
monolinguals = questionnaire_data[questionnaire_data$bilingual == 0, ]
bilinguals = questionnaire_data[questionnaire_data$bilingual != 0, ]
```

## The Approach

An experimenter supervised questionnaire was administered
to ``r nrow(questionnaire_data)`` volunteer participants.
The questionnaire was supervised to ensure 
a reasonable completion rate
and to ensure the participants understood the questions being asked.
In in the event
some of the questions were challenging for the participants to understand.
If a similar questionnaire were to be administered without supervision
it would need further refinement to allow the participants to complete
it successfully.

The questionnaire consisted of 3 parts.

1. Rating Scales - participants were asked to rate 
   their coffee and cake experience on 7 arbitrary scales.
1. Word Assignment - participants were asked to indicate which words from a list
   (7 positive, 7 negative and 7 neutral) 
   could be applied to their coffee and cake experience.
1. A Cloze Procedure - participants were asked to fill in the blanks
   in a sentence from Tolstoy's 'Anna Karenina'.


# The Participants

The participants were all volunteers
selected from the experimenter's friends and family.
This is an undoubtedly biased sample, 
but using an entirely randomly selected sample
would have been too complicated and costly.

## Age

```{r}
mean_age = mean(questionnaire_data$age, trim = 0, na.rm = FALSE)
```

Average age is ``r round(mean_age, digits = 1)``.
So the sample is largely middle aged and post retirment.

```{r}
hist(questionnaire_data$age, 
     main = "",
     xlab="Age in Years", 
     ylab="Count",
     col="darkmagenta",
     freq=TRUE
     )
```

## Gender

The sample was intended to be gender balanced,
but ended up with more females.

```{r}
gender = table(questionnaire_data$gender)
pie(gender, 
    c("Female", "Male"),
    main = "", 
    col = rainbow(length(gender))
    )
```

## Second Language

A total of ``r nrow(questionnaire_data)`` participants took part in the study,
``r nrow(monolinguals)`` of whom spoke only English
and
``r nrow(bilinguals)``of whom spoke English and one other language.

Mostly North European languages with strong coffee and cake cultures.
Half the participants were bilingual and half were monolingual.
Unsurprisingly given that the study was conducted in England,
the second languages spoken were all from Northern European nations.

```{r}
languages <- table(questionnaire_data$language)
languages
```

# Do the two groups have different concepts of coffee and cake?

The data were split the data into those who speak a second language
and those that do not.

## Difference in Rating

Participants found rating their coffee and cake experience 
on a set of arbitrary scales challenging.
Some of the scales made no obvious sense to the participants
so placing a numerical value against that scale 
was equally non-sensical.
It was necessary to encourage participants to attempt an 'intuitive'
or 'gut feeling' response.

The hypothesis was that participants with a second language would
have a broader concept of their coffee and cake experience.
This would be expected to show up with the participants with a second language,
providing more variable ratings for their coffee and cake experience.
Whilst those with a single language might consistently
rate their coffee and cake experience at one end of the scale.

As can see seen below,
in every case there is little or nothing to distinguish between
the two groups of participants.
This is confirmed by means of an F-test.

It may be that participants were choosing a random number to be able to answer the question.
However, this was not evident during the administration of the questionnaire.
Each of the participants appear to give the rating scales some thoughtful consideration.
This is born out in the distributions shows below,
in that they do not appear to be random
and the two groups of participants appear to be consistent.

It would seem that when forced to rate their coffee and cake experience,
both those with a second language and those without rate
their experience similarly.

```{r}
# Double histogram for comparing the rating scales
library("colorspace") # for lighten and darken
rating.double.histogram <- function(monolingual.scale, bilingual.scale, colour="blue") 
{
    par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
    monolingual.breaks <- seq(min(monolingual.scale)-0.5, max(monolingual.scale)+0.5, by=1)
    monolingual.colour <- lighten(colour, 0.4)
    hist(monolingual.scale,
         breaks=monolingual.breaks,
         col=monolingual.colour,
         freq=TRUE,
         main="No Second Language",
         xlab="",
         xlim=c(1,7),
         ylim=c(0,4)
         )
    bilingual.breaks <- seq(min(bilingual.scale)-0.5, max(bilingual.scale)+0.5, by=1)
    bilingual.colour <- darken(colour, 0.4)
    hist(bilingual.scale,
         breaks=bilingual.breaks,
         col=bilingual.colour,
         freq=TRUE,
         main="With Second Language",
         xlab="",
         xlim=c(1,7),
         ylim=c(0,4)
         )
}
```

### Hot-Cold

```{r}
rating.double.histogram(monolinguals$cold.hot, bilinguals$cold.hot, "violet")
var.test(monolinguals$cold.hot, bilinguals$cold.hot, alternative = "two.sided")
```

### Fat-Thin

```{r}
rating.double.histogram(monolinguals$fat.thin, bilinguals$fat.thin, "purple")
var.test(monolinguals$fat.thin, bilinguals$fat.thin, alternative = "two.sided")
```

### Funny-Sad

```{r}
rating.double.histogram(monolinguals$funny.sad, bilinguals$funny.sad, "blue")
var.test(monolinguals$funny.sad, bilinguals$funny.sad, alternative = "two.sided")
```

### Red-Green

```{r}
rating.double.histogram(monolinguals$red.green, bilinguals$red, "green")
var.test(monolinguals$red.green, bilinguals$red, alternative = "two.sided")
```

### Horrible-Fantastic

```{r}
rating.double.histogram(monolinguals$horrible.fantastic, bilinguals$horrible.fantastic, "yellow")
var.test(monolinguals$horrible.fantastic, bilinguals$horrible.fantastic, alternative = "two.sided")
```

### Stupid-Intellectual

```{r}
rating.double.histogram(monolinguals$stupid.intellectual, bilinguals$stupid.intellectual, "orange")
var.test(monolinguals$stupid.intellectual, bilinguals$stupid.intellectual, alternative = "two.sided")
```

### Sparkling-Still

```{r}
rating.double.histogram(monolinguals$sparkling.still, bilinguals$sparkling, "red")
var.test(monolinguals$sparkling.still, bilinguals$sparkling, alternative = "two.sided")
```

## Word Assignment

It was readily apparent during the administration of the questionnaires,
that the participants could easily determine which word
could be applied to their coffee and cake experience.

If the hypothesis is correct that those with a second language would have
a broader concept of coffee and cake.
As a result one would expect them to select more words from the word list
to reflect their broader concept.

Taking the total number of words selected
it is clear that those with a second language consistently selected
more words than those without a second language.

```{r}
assignment.double.histogram <- function(monolingual.scale, bilingual.scale, colour="blue") 
{
    par(mfrow=c(1,2))    # set the plotting area into a 1*2 array
    monolingual.breaks <- seq(min(monolingual.scale)-0.5, max(monolingual.scale)+0.5, by=1)
    monolingual.colour <- lighten(colour, 0.4)
    hist(monolingual.scale,
         breaks=monolingual.breaks,
         col=monolingual.colour,
         freq=TRUE,
         main="No Second Language",
         xlab="",
         xlim=c(1,12),
         ylim=c(0,4)
         )
    bilingual.breaks <- seq(min(bilingual.scale)-0.5, max(bilingual.scale)+0.5, by=1)
    bilingual.colour <- darken(colour, 0.4)
    hist(bilingual.scale,
         breaks=bilingual.breaks,
         col=bilingual.colour,
         freq=TRUE,
         main="With Second Language",
         xlab="",
         xlim=c(1,12),
         ylim=c(0,4)
         )
}
assignment.double.histogram(monolinguals$total_selected, bilinguals$total_selected)
```

The average for those with a second language was ``r mean(bilinguals$total_selected)``
where as for those without a second language the average was
``r mean(monolinguals$total_selected)``.
Using an F-test this is confirmed to be a statistically significant difference.

```{r}
var.test(bilinguals$total_selected, monolinguals$total_selected, alternative = "two.sided")
```
### Word Cloud

Looking at word cloud of the most popular words choosen,
it appears that the positive words were favoured over the negative and neutral words.
It is clear that all the participants
have a positive conceptualization of their coffee and cake experience.

```{r}
library(tidyverse)
library(RColorBrewer)
library(wordcloud)
library(dplyr)
pick_columns = questionnaire_data %>% select(8:28)
pick_counts = colSums(pick_columns)
pick_counts =  as.data.frame(as.table(pick_counts))
wordcloud(words=pick_counts$Var1, freq=pick_counts$Freq,
          max.words=12, random.order=FALSE,
          min.freq=4, colors=brewer.pal(8, "Dark2"))
```

### Positive Words

Indeed it is clear that the difference between
those with a second language and those without
is driven by the positive words.
This is demonstrated to be statistically significant using an F-test.

```{r}
assignment.double.histogram(monolinguals$total_selected_positive, bilinguals$total_selected_positive)
var.test(monolinguals$total_selected_positive, bilinguals$total_selected_positive, alternative = "two.sided")
```

### Neutral Words

However there is no significant difference between the two groups
based on their selections of neutral words.

```{r}
assignment.double.histogram(monolinguals$total_selected_neutral, bilinguals$total_selected_neutral, "red")
var.test(monolinguals$total_selected_neutral, bilinguals$total_selected_neutral, alternative = "two.sided")
```

Neither group selected sufficient of the negative words to draw any inferences.

It is apparent that the group of participants with a second language
did select more positive words to describe their coffee and cake
experience that those without a second language.

### For Cloze Procedure

Completing the Cloze procedure was clearly those most challenging task
for all the participants in the study.
None of them was sufficiently familiar with the extract from 
'Anna Karenina' to complete the original sentence
and 
all the participants required a great deal of encouragement.
Only one word was chosen by two different participants (red)
but it is hard to ascribe anything meaningful to this result.
One is forced to conclude that most of the participants
simply choose a random word it order to be able to complete the task
and that any priming concerning coffee and cake
was overwhelmed by a desire to complete the task.

